I don't know if projection is categorical. \\ Did \citealt{mandelkern-etal2020} discover that it is?

### 2023-12-08 output/naturalness-paper/paper.tex
updated paper

These observations were confirmed by a posthoc pairwise comparison of the naturalness ratings of the contents associated with the six controls and 20 target expressions in the explicit ignorance context using the `emmeans' package (\citealt{emmeans}) in R (\citealt{r}). The input to the pairwise comparison was a Bayesian mixed-effects beta regression model with weakly informative priors that was fitted using the `brms' package (\citealt{buerkner2017}). The model predicted naturalness ratings from a fixed effect of expression (with treatment coding and `continue' as reference level) and included random by-participant and by-item intercepts (where an item is a complement clause). The output of the pairwise comparison were 95\% highest density intervals (hdis) of estimated marginal mean differences between each of the 26 contents. We assume that two contents differ in their naturalness in the explicit ignorance context if their hdi does not include 0.

@@

These observations were confirmed by posthoc pairwise comparisons of the naturalness ratings in the three contexts for each of the 20 predicates, again using the `emmeans' package (\citealt{emmeans}). The input to the pairwise comparisons were 20 Bayesian mixed-effects beta regression models with weakly informative priors that were fitted using the `brms' package (\citealt{buerkner2017}). The models predicted, for each predicate, the naturalness ratings from a fixed effect of context (with treatment coding and `explicit ignorance' as reference level) and included random by-item intercepts. The output of the pairwise comparison are 95\% hdis of estimated marginal mean differences between each of the three contexts for each of the 20 contents. We assume that the naturalness ratings between two contexts differ if their hdi does not include 0.\footnote{The full model output is available here: \url{LINK TO TABLE IN REPO}.{\bf ADD AFTER FINALIZING SCRIPTS}} As shown in Fig.~\ref{fig:acc-by-context}, naturalness ratings in explicit ignorance vs.\ lower or higher prior probability contexts do not provide support for a categorical distinction between presuppositions and nonpresuppositions.

>>>>

These observations were confirmed by a posthoc pairwise comparison of the naturalness ratings of the contents associated with the six controls and 20 target expressions in the explicit ignorance context using the `emmeans' package (\citealt{emmeans}) in R (\citealt{r}). The input to the pairwise comparison was a Bayesian mixed-effects beta regression model with weakly informative priors that was fitted using the `brms' package (\citealt{buerkner2017}). The model predicted naturalness ratings\footnote{To model the ratings using a beta regression, the ratings were first transformed from the interval [0,1] to the interval (0,1) using the method proposed in \citealt{smithson-verkuilen2006}.} from a fixed effect of expression (with treatment coding and `continue' as reference level) and included random by-participant and by-item intercepts (where an item is a complement clause). The output of the pairwise comparison were 95\% highest density intervals (hdis) of estimated marginal mean differences between each of the 26 contents. We assume that two contents differ in their naturalness in the explicit ignorance context if their hdi does not include 0.

@@

These observations were confirmed by posthoc pairwise comparisons of the naturalness ratings in the three contexts for each of the 20 predicates, again using the `emmeans' package (\citealt{emmeans}). The input to the pairwise comparisons were 20 Bayesian mixed-effects beta regression models with weakly informative priors that were fitted using the `brms' package (\citealt{buerkner2017}). The models predicted, for each predicate, the naturalness ratings\footnote{As in the model reported above, the ratings were transformed to the interval (0,1).} from a fixed effect of context (with treatment coding and `explicit ignorance' as reference level) and included random by-item intercepts. The output of the pairwise comparison are 95\% hdis of estimated marginal mean differences between each of the three contexts for each of the 20 contents. We assume that the naturalness ratings between two contexts differ if their hdi does not include 0.\footnote{The full model output is available here: \url{LINK TO TABLE IN REPO}.{\bf ADD AFTER FINALIZING SCRIPTS}} As shown in Fig.~\ref{fig:acc-by-context}, naturalness ratings in explicit ignorance vs.\ lower or higher prior probability contexts do not provide support for a categorical distinction between presuppositions and nonpresuppositions.
